---
title: "Monte Carlo Simulations"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

The code bellow summarizes and presents the result of Monte Carlo power simulations for the main model presented in our preregistration.

The following code loads and reformats the simulation output:

```{r}
load("simulation1.RData")

sim_results <- simulation1 %>%
               t %>%
               as.data.frame(stringsAsFactors = FALSE)
sim_results[[1]] <-as.numeric(sim_results[[1]])
sim_results[[2]] <-as.numeric(sim_results[[2]])
sim_results[[3]] <-as.numeric(sim_results[[3]])
sim_results[[4]] <-as.numeric(sim_results[[4]])
sim_results[[5]] <-as.numeric(sim_results[[5]])
sim_results[[6]] <-as.numeric(sim_results[[6]])
sim_results[[7]] <-as.numeric(sim_results[[7]])


```

## Results

The following code summarizes the result of a power simulation conducted for the full model:

y_simulated ~ effort * social_inequality + (social_inequality || subject) + (effort * social_inequality || species) + (social_inequality || paper)

Covariates were taken from a preliminary list of 25 eligible papers and can be found in covaraites_table.csv.

Fixed effects were simulated based on a priori rejection probabilities found in the file test_probabilities.csv.

Random effects were simulated based on the intercept and slope structure of the maximal model, according to SD estimates found in simulation_code_savio.R.

P-value of model comparison refers to this restricted model:

y_simulated ~ effort + (social_inequality || subject) + (effort * social_inequality || species) + (social_inequality || paper)


```{r}

print(paste("Number of iterations: ", nrow(sim_results), sep = ""))

percent_converged = sum(nchar(sim_results$warnings) == 0) / length(sim_results$warnings) * 100
  
print(paste("Percent of models that converged without errors: ", percent_converged, "%", sep = ""))
  
significant_positive_interaction = mean(as.numeric(sim_results$`p(effort:social_inequality)` < 0.05 & nchar(sim_results$warnings) == 0 & sim_results$b_effortXsocial_inequality > 0)) * 100
  
print(paste("Models that converged with a significant positive interaction of effort and social_inequality: ", significant_positive_interaction, "%", sep = ""))
  
significant_comparison = mean(as.numeric(sim_results$`p(model comparison)`) < 0.05 & nchar(sim_results$warnings) == 0 & sim_results$b_social_inequality > 0) * 100
  
print(paste("Models that converged with a significant model comparison and a positive effect of social_inequality: ", significant_comparison, "%", sep = ""))
  
print(paste("Estimated coefficient for intercept: M = ", round(mean(sim_results$b_intercept), digits = 3), ", SD = ", round(sd(sim_results$b_intercept), digits = 3), sep = ""))

print(paste("Estimated coefficient for social_inequality: M = ", round(mean(sim_results$b_social_inequality), digits = 3), ", SD = ", round(sd(sim_results$b_social_inequality), digits = 3), sep = ""))
  
print(paste("Estimated coefficient for effort: M = ", round(mean(sim_results$b_effort), digits = 3), ", SD = ", round(sd(sim_results$b_effort), digits = 3), sep = ""))

print(paste("Estimated coefficient for interaction of effort and social inequality: M = ", round(mean(sim_results$b_effortXsocial_inequality), digits = 3), ", SD = ", round(sd(sim_results$b_effortXsocial_inequality), digits = 3), sep = ""))
  
print(c("All warnings:", sim_results$warnings[which(nchar(sim_results$warnings) > 0)]))

```


### Results with fixed effects set to 0

To get a rough estimate of the Type I error rate, we also conducted the same analysis with the fixed effects set to 0:


```{r}
load("simulation2_h0.RData")

sim_results_h0 <- simulation1 %>%
               t %>%
               as.data.frame(stringsAsFactors = FALSE)
sim_results_h0[[1]] <-as.numeric(sim_results_h0[[1]])
sim_results_h0[[2]] <-as.numeric(sim_results_h0[[2]])
sim_results_h0[[3]] <-as.numeric(sim_results_h0[[3]])
sim_results_h0[[4]] <-as.numeric(sim_results_h0[[4]])
sim_results_h0[[5]] <-as.numeric(sim_results_h0[[5]])
sim_results_h0[[6]] <-as.numeric(sim_results_h0[[6]])
sim_results_h0[[7]] <-as.numeric(sim_results_h0[[7]])

print(paste("Number of iterations: ", nrow(sim_results_h0), sep = ""))

percent_converged = sum(nchar(sim_results_h0$warnings) == 0) / length(sim_results_h0$warnings) * 100
  
print(paste("Percent of models that converged without errors: ", percent_converged, "%", sep = ""))
  
significant_positive_interaction = mean(as.numeric(sim_results_h0$`p(effort:social_inequality)` < 0.05 & nchar(sim_results_h0$warnings) == 0 & sim_results_h0$b_effortXsocial_inequality > 0)) * 100
  
print(paste("Models that converged with a significant positive interaction of effort and social_inequality: ", significant_positive_interaction, "%", sep = ""))
  
significant_comparison = mean(as.numeric(sim_results_h0$`p(model comparison)`) < 0.05 & nchar(sim_results_h0$warnings) == 0 & sim_results_h0$b_social_inequality > 0) * 100
  
print(paste("Models that converged with a significant model comparison and a positive effect of social_inequality: ", significant_comparison, "%", sep = ""))
  
print(paste("Estimated coefficient for intercept: M = ", round(mean(sim_results_h0$b_intercept), digits = 3), ", SD = ", round(sd(sim_results_h0$b_intercept), digits = 3), sep = ""))

print(paste("Estimated coefficient for social_inequality: M = ", round(mean(sim_results_h0$b_social_inequality), digits = 3), ", SD = ", round(sd(sim_results_h0$b_social_inequality), digits = 3), sep = ""))
  
print(paste("Estimated coefficient for effort: M = ", round(mean(sim_results_h0$b_effort), digits = 3), ", SD = ", round(sd(sim_results_h0$b_effort), digits = 3), sep = ""))

print(paste("Estimated coefficient for interaction of effort and social inequality: M = ", round(mean(sim_results_h0$b_effortXsocial_inequality), digits = 3), ", SD = ", round(sd(sim_results_h0$b_effortXsocial_inequality), digits = 3), sep = ""))
  
print(c("All warnings:", sim_results_h0$warnings[which(nchar(sim_results_h0$warnings) > 0)]))

```